Data preparation

### 2023-10-29 procesamiento/prod_analysis.Rmd
medidas de clase social

>>>>

# Check on homogeneity

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,haven,sjmisc,GGally,ggplot2)
load(here::here("input/data/proc/study1_country.RData"))

test <- df2

frq(df2$class11d)

test$egp3_v1 <- car::recode(test$class11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
test$egp3_v2 <- car::recode(test$digclass11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
test$egp3_v3 <- car::recode(test$dclass11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))

frq(test$egp3_v1)
frq(test$egp3_v2)
frq(test$egp3_v3)
frq(test$class3)

test$ingroup1 <- NA 
test$ingroup1 <- ifelse(test$egp3_v1==1,test$n_high,test$ingroup1)
test$ingroup1 <- ifelse(test$egp3_v1==2,test$n_middle,test$ingroup1)
test$ingroup1 <- ifelse(test$egp3_v1==3,test$n_low,test$ingroup1)

test$ingroup2 <- NA 
test$ingroup2 <- ifelse(test$egp3_v2==1,test$n_high,test$ingroup2)
test$ingroup2 <- ifelse(test$egp3_v2==2,test$n_middle,test$ingroup2)
test$ingroup2 <- ifelse(test$egp3_v2==3,test$n_low,test$ingroup2)

test$ingroup3 <- NA 
test$ingroup3 <- ifelse(test$egp3_v3==1,test$n_high,test$ingroup2)
test$ingroup3 <- ifelse(test$egp3_v3==2,test$n_middle,test$ingroup2)
test$ingroup3 <- ifelse(test$egp3_v3==3,test$n_low,test$ingroup2)

test$homclass_v1 <- as.numeric(test$ingroup1/test$know_total)

test$homclass_v2 <- as.numeric(test$ingroup2/test$know_total)

test$homclass_v3 <- as.numeric(test$ingroup3/test$know_total)

sjPlot::plot_frq(test$homclass_v1,type = "density")
sjPlot::plot_frq(test$homclass_v2,type = "density")
sjPlot::plot_frq(test$homclass_v3,type = "density")
sjPlot::plot_frq(df2$homclass)
```

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- test %>% dplyr::select(
                        class3=class6,
                        homclass=homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  na.omit()

# Models 
base <- lmer(homclass~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +class3)
full1 <- update(homclass, . ~ . + female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
knitreg(list(homclass,full1,rob1))
```

### 2023-10-29 procesamiento/prod_prep.Rmd
medidas de clase social

# Class Scheme 3 classes
df1$class3 <- car::recode(df1$class11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV)';
                             8:11='Working Class (V+VI+VII)'")

>>>>

# Class Scheme 3 classes
df1$class3 <- car::recode(df1$class11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")
